### 2016-09-29 rebuttal.tex

Moreover, these vastly differently approached elements come in no specific
order, and with no obvious reason why each of them is picked to be covered at
all and, specifically, at the chosen level of complexity in the approach.

I suggest a major rewrite of the paper, to improve the structure and group differently approached subjects. It would probably be best to:
\begin{enumerate}
\item Create a new section (following the introduction of SymPy) on projects that use SymPy, and put in it the materials currently available in supplement's sections 8, 9, 11. The comparison with Mathematica (supplement's section 10) should be moved either to the introduction as a section, or right after the introduction as its own section, but it should not be in the middle of the description of SymPy-powered projects.
\item  This should be followed by the list of SymPy packages and modules (currently section 3) and descriptions of selected modules (currently sections 3.1, 3.3, 3.5, supplement's sections 5, 7, and 9).
\item Now, basic usage can be given as its own section (currently done in sections 2.1 and 2.3), followed by introductions on usage of various modules (currently in sections 3.2, 3.4, 3.6, 4, 5, and supplement's sections 2, 3, 4, 6).
\item In-depth architecture (most of the so far unmentioned sections) can be given either as its own section, or made into a supplement of its own (as it is naturally far more technical and less interesting to general audience).
\item The current conclusion works fine as the finishing section of the paper.
\end{enumerate}
\begin{solution}
  We have made the following changes to the paper

  \begin{enumerate}
  \item We have renamed the ``Features'' section to ``Overview of
    Capabilities'', now section~\ref{P-sec:features}.
  \item We have renamed the ``Domain Specific Submodules'' section to
      ``Physics Submodule'', now section~\ref{P-sec:domain_specific} (see point~\ref{rev3point30}).
  \item We have moved the ``Architecture'' section to the end, after the
    ``Physics Submodule'' section. It is now section~\ref{P-sec:architecture}.
  \item We have moved the ``Basic Usage'' subsection to the beginning of the
    ``Overview of Capabilities'' section (it is now section~\ref{P-sec:basic-usage}), and added an intro paragraph to the
    ``Overview of Capabilities'' section.
  \item We have moved the ``Assumptions'' subsection to the ``Overview of
    Capabilities'' subsection, after the features table. It is now section~\ref{P-sec:assumptions}.
  \item The ``Comparison with Mathematica'' section has been moved to the end of
    the supplement, now section~\ref{S-suppsec:comp-mma}.
  \item The ``Other Projects that
      Depend on SymPy'' section (which has been renamed from ``Other Projects that
      Use SymPy'') has been moved from the supplement to the main paper
      content, now section~\ref{sec:other-proj}.
  \end{enumerate}

### 2016-09-29 rebuttal.tex

Moreover, these vastly differently approached elements come in no specific
order, and with no obvious reason why each of them is picked to be covered at
all and, specifically, at the chosen level of complexity in the approach.

I suggest a major rewrite of the paper, to improve the structure and group differently approached subjects. It would probably be best to:
\begin{enumerate}
\item Create a new section (following the introduction of SymPy) on projects that use SymPy, and put in it the materials currently available in supplement's sections 8, 9, 11. The comparison with Mathematica (supplement's section 10) should be moved either to the introduction as a section, or right after the introduction as its own section, but it should not be in the middle of the description of SymPy-powered projects.
\item  This should be followed by the list of SymPy packages and modules (currently section 3) and descriptions of selected modules (currently sections 3.1, 3.3, 3.5, supplement's sections 5, 7, and 9).
\item Now, basic usage can be given as its own section (currently done in sections 2.1 and 2.3), followed by introductions on usage of various modules (currently in sections 3.2, 3.4, 3.6, 4, 5, and supplement's sections 2, 3, 4, 6).
\item In-depth architecture (most of the so far unmentioned sections) can be given either as its own section, or made into a supplement of its own (as it is naturally far more technical and less interesting to general audience).
\item The current conclusion works fine as the finishing section of the paper.
\end{enumerate}
\begin{solution}
  We have made the following changes to the paper

  \begin{enumerate}
  \item We have renamed the ``Features'' section to ``Overview of
    Capabilities'', now section~\ref{P-sec:features}.
  \item We have renamed the ``Domain Specific Submodules'' section to
      ``Physics Submodule'', now section~\ref{P-sec:domain_specific} (see point~\ref{rev3point30}).
  \item We have moved the ``Architecture'' section to the end, after the
    ``Physics Submodule'' section. It is now section~\ref{P-sec:architecture}.
  \item We have moved the ``Basic Usage'' subsection to the beginning of the
    ``Overview of Capabilities'' section (it is now section~\ref{P-sec:basic-usage}), and added an intro paragraph to the
    ``Overview of Capabilities'' section.
  \item We have moved the ``Assumptions'' subsection to the ``Overview of
    Capabilities'' subsection, after the features table. It is now section~\ref{P-sec:assumptions}.
  \item The ``Comparison with Mathematica'' section has been moved to the end of
    the supplement, now section~\ref{S-suppsec:comp-mma}.
  \item The ``Other Projects that
      Depend on SymPy'' section (which has been renamed from ``Other Projects that
      Use SymPy'') has been moved from the supplement to the main paper
      content, now section~\ref{P-sec:other-proj}.
  \end{enumerate}

### 2016-09-29 supplement.tex
Rename \label{comp-mma} to \label{suppsec:comp-mma}
Fix Mathematica section \ref
Rename SymPy Gamma label

The supplementary material take a deeper look at certain topics in SymPy for
which there was not enough room to discuss in the paper.
Section~\ref{suppsec:Gruntz} discusses the Gruntz algorithm, used to
calculate limits in the SymPy.  Sections~\ref{suppsec:Series}--\ref{suppsec:Ten}
discuss in depth some selected submodules.  Section~\ref{suppsec:numsimpl}
discusses numerical simplification.  Section~\ref{suppsec:examples} provides
additional examples for topics, discussed in the main paper.  In section
\ref{sympy-gamma} the SymPy Gamma
and the SymPy Live projects are introduced.  Finally, section \ref{comp-mma}
has a
brief comparison of SymPy with Wolfram Mathematica.

@@

\section{SymPy Gamma}\label{sympy-gamma}

\input{gamma}

\section{Comparison with Mathematica}
\label{comp-mma}
\input{comparison_with_mma}

>>>>

The supplementary material take a deeper look at certain topics in SymPy for
which there was not enough room to discuss in the paper.
Section~\ref{suppsec:Gruntz} discusses the Gruntz algorithm, used to
calculate limits in the SymPy.  Sections~\ref{suppsec:Series}--\ref{suppsec:Ten}
discuss in depth some selected submodules.  Section~\ref{suppsec:numsimpl}
discusses numerical simplification.  Section~\ref{suppsec:examples} provides
additional examples for topics, discussed in the main paper.  In section
\ref{suppsec:sympy-gamma} the SymPy Gamma
and the SymPy Live projects are introduced.  Finally, section~\ref{suppsec:comp-mma}
has a
brief comparison of SymPy with Wolfram Mathematica.

@@

\section{SymPy Gamma}
\label{suppsec:sympy-gamma}
\input{gamma}

\section{Comparison with Mathematica}
\label{suppsec:comp-mma}
\input{comparison_with_mma}
